\documentclass[10pt,letterpaper,titlepage]{article}
\usepackage{titletoc}

\usepackage{ifthen,varioref}
\usepackage{url}
\usepackage{titlesec}
\usepackage{fullpage}
\usepackage{hyperref}

% fix block paragraphs in toc
\usepackage{parskip}
% use block paragraphs
\setlength{\parindent}{0pt}
%\setlength{\parskip}{\baselineskip}
\setlength{\parskip}{4pt}

\newcommand\corpname{Gainesville Hackerspace, Inc.}
\newcommand\approvaldate{March 9, 2010}

\hypersetup{
    pdfauthor={Ian Taylor},
    pdftitle={\corpname{} Bylaws},
    pdfborder={0 0 0},
    pdfsubject={bylaws},
    pdfkeywords={bylaws, \corpname},
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue,
    bookmarks=true,
    colorlinks=false
}

\titlecontents{section}[1.5em]
    {}
    {\contentslabel{2.0em}}
    {\hspace*{-2.0em}}
    {\titlerule*[1pc]{.}\contentspage}

\renewcommand\thesection{\Roman{section}}
\renewcommand\thesubsection{\arabic{subsection}}
\titleformat{\section}{\bfseries\Large}{Article~\thesection}{0.5em}{}
\titleformat{\subsection}{\bfseries\large}{Section~\thesubsection}{0.5em}{}
\labelformat{section}{Article~#1}
\labelformat{subsection}{\protect\iscurrentsection{\thesection}Section~#1}
\newcommand\iscurrentsection[1]{%
    \ifthenelse{\equal{#1}{\thesection}}{}{Article~#1~}}

% for things like 1\st 2\nd 3\rd 4\th
\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
\renewcommand{\th}[0]{\superscript{th}}
\newcommand{\st}[0]{\superscript{st}}
\newcommand{\nd}[0]{\superscript{nd}}
\newcommand{\rd}[0]{\superscript{rd}}

\author{}
\title{%
    \textsc{\LARGE \corpname \\
    \Large Bylaws
    }
}
\date{March 9, 2010}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{Why We Exist}
\label{whyweexist}

By law, this is the core governing document of \corpname{}

These Bylaws were approved by the incorporators on \approvaldate{} after
consulting with founding members.

\subsection{General Purposes}
\label{genpurp}

Said corporation is organized exclusively for charitable, educational, and
scientific purposes within the meaning of Section 501(c)(3) of the Internal
Revenue Code, or the corresponding subsection of any future federal tax code.
The mission of the corporation is to improve the world by creatively rethinking
technology.

\subsection{Specific Purposes}

Subject to and within the limits of \ref{genpurp}, the corporation shall:
\begin{itemize}
    \item Build or lease and maintain spaces suitable for technical, artistic,
          and social collaboration.

    \item Collaborate on all forms of technology, culture, and craft in new and
          interesting ways.

    \item Apply the results of its work to cultural, charitable and
          scientific causes.

    \item Share its research and discoveries, using what is learned to
          teach others.

    \item Recruit and develop members to participate in these activities.
\end{itemize}

\section{Who We Are}

\subsection{Designation of Membership Types}

\corpname{} has basic and voting members.

\subsection{Basic Membership Election}

Any person who supports the purposes laid out in \ref{whyweexist} of
these bylaws is qualified to become a basic member.  Any qualified person
may be elected a basic member upon payment of appropriate dues and by a simple
majority of a quorum of voting members.


\subsection{Voting Membership Election}

Any basic member whose dues are current is qualified to become a voting
member. Any voting member may nominate a basic member to be a voting
member. Any eligible person may be elected as a voting member at a
regular meeting by three quarters of all voting members.
For purposes of these bylaws, all founding members shall be considered
the initial voting members.


\subsection{Membership Dues}
\label{votmemdue}

The amount, payment period, due date and acceptable methods for collection of
dues shall be reviewed each year at the annual meeting.
A majority vote of the voting members at the annual meeting may change the procedure
and terms for payment of dues.
A member may request that their membership be put in suspension for a maximum
of 3 months.

\subsection{Basic Membership Rights and Responsibilities}
% redundant with 'Basic Membership Election' section
% Basic memberships and membership titles are subject to voting member approval.

Each basic member has the right to:
\begin{itemize}
    \item Access the space 24 hours a day, 7 days a week.

    \item Use equipment and supplies purchased by the corporation for purposes
        subject to and within the limits of \ref{whyweexist}.
\end{itemize}

Each basic member has the responsibility to:
\begin{itemize}
    \item Pay dues in a timely manner.

    \item Provide current address, contact information, and preference for
        electronic receipt of communications.

    \item Continue to support the purposes of the corporation.
\end{itemize}

\subsection{Voting Membership Rights and Responsibilities}
Each voting member has all the rights and responsibilities of a basic member.

Additionally, voting members have the right to:
\begin{itemize}
    \item Exercise a single vote for each decision put before the voting
        membership.

    \item Reasonable inspection of corporate records.

    \item Voice opinion and vote preference or abstain from voting in the
        affairs put before the voting membership.
\end{itemize}

\subsection{Membership Resignation and Termination}
% this should probably be turned into a list so it's easier to read
Any member may resign by filing a written resignation with the
Secretary.
Resignation shall not relieve a member of unpaid dues or other monies
owed.
Membership may be suspended for non-payment of dues by the Treasurer.
Any suspended member may restore their membership up to 90 days after
suspension upon payment of dues owed and payable through one month beyond the
end of the suspension period.
Once the 90 days of non-payment have passed, the membership is automatically
terminated.
Any membership may also be terminated for any reason by written petition
signed by more than three quarters of the voting members.


\section{Meetings}

\subsection{Regular Meetings}

Regular meetings of voting members shall be held every Tuesday at 19:00 local
time at the registered office.
A different meeting place may be designated by written petition signed by more
than three quarters of voting members.
Regular meetings shall not take place on the day before, upon, or after a
federal holiday unless specifically approved at the prior regular meeting or
annual meeting.
Meetings shall not take place on the day of a closure declared by the Office of
Personnel Management.

\subsection{Annual Meetings}

An annual meeting of all members shall take place sometime in January, February
or March.
The Board of Directors shall select the date, time and place no later than
January 31 of each year.
The date, time, and place of the annual meeting must be posted in the registered
office and submitted to members electronically at least two weeks prior to the
annual meeting.
A petition signed by more than three quarters of voting members
and submitted to the Board of Directors before President's Day may specify a
new date, time, and place for the annual meeting.
At the annual meeting, the voting members shall elect the Board of Directors,
review and vote on the standing rules and policies of the corporation, receive
reports on the activities of the corporation, approve the budget, and determine
the direction of the corporation in the coming year.

\subsection{Special Meetings}
\label{specialmeet}

A petition presented to all voting members and signed by one third of voting
members may call a special meeting.  Such a petition must include the date,
time, place, and agenda of the special meeting.

\subsection{Notice of Meetings}

The time and place of upcoming meetings shall be conspicuously posted at the
registered office and electronically sent to all voting members.
No notice is required for a regular meeting.
Special meetings require 72 hours notice considered delivered only when all
voting members are personally notified and given an opportunity to sign a
special meeting petition.
The agenda of the next upcoming meeting and minutes of the previous meeting
shall be posted at the registered office and electronically submitted to all
voting members at least 72 hours prior to any meeting.

\subsection{Quorum}

At a duly called meeting, at least one half of the entire voting
membership shall constitute a quorum.

\subsection{Voting}

When a quorum is present, all issues, except when otherwise specified in these
bylaws, shall be decided by affirmative vote of more than one half of the
voting members present.

\subsection{Conduct of Meetings}
\label{condofmeet}

All meetings shall follow the Robert's Rules of Order as approved at an annual
meeting.


\section{The Officers}
\label{officers}

\subsection{Role, Number, Qualification, Term and Compensation}

There shall be five officers consisting of President, Vice President,
Secretary, Treasurer, and Sergeant at Arms.
Each officer must be a director and each officer shall serve from the time of
their election until their successor is elected and qualifies.
A term shall begin at the conclusion of the annual meeting as defined in
\ref{specialmeet} and shall last until the next annual meeting.
No officer shall be compensated for their service as an officer, though the
corporation may provide insurance and indemnity for officers as allowed by law.

\subsection{Duties of the President}

The President shall preside over all meetings or designate an alternate,
attempt to achieve consensus in all decision-making, ensure the membership is
informed of all relevant issues, and serve all other duties of a President as
required by law or custom.

\subsection{Duties of the Vice President}

The Vice President shall be primarily responsible for the information systems
and communication processes of the corporation, coordinate the teams that
manage and design those systems, draft policies and procedures for information
system use, ensure effective communication and information exchange within the
corporation, and serve all other duties of a Vice President as required by
law or custom, including acting when the President is unable or unwilling to
act.

\subsection{Duties of the Secretary}

The Secretary shall be responsible for membership records including membership
and board meeting actions and petitions, sending out meeting announcements,
posting and distributing copies of membership meeting minutes and relevant
meeting agendas to the membership, assuring that corporate records are
maintained, and serving all other duties of a Secretary as required by law or
custom.

\subsection{Duties of the Treasurer}

The Treasurer shall be custodian of corporate funds, collect dues, make a
financial report for each meeting, assist in the preparation of the budget,
develop fundraising plans, make financial information available to members and
the public, sneer at members who do not pay dues in a timely fashion, and serve
all other duties of a Treasurer as required by law or custom.

\subsection{Duties of the Sergeant at Arms}

The Sergeant at Arms shall ensure that order is kept and that everyone upholds
the rules outlined in \ref{condofmeet} are upheld at all meetings.

\subsection{Duties of the Officers as a Whole to Provide an Annual Report}

The Officers must prepare an annual report to be distributed at the annual
meeting.
The report should chronicle the activities of the corporation, including
specific narratives on the corporation's work, the corporation's annual
financial statements, relevant legal filings, and relevant copies of the
organization's district and federal tax returns.

\subsection{Officers are Directors}

The officers shall also serve as bona-fide directors on the Board of Directors.
Election, resignation, removal and vacancies of the officers are handled in
accordance with procedures laid out in \ref{boardofdirect}.

\section{The Board of Directors}
\label{boardofdirect}

\subsection{Role, Size, Term, and Compensation}

The Board of Directors shall consist of the five officers as defined in
\ref{officers}, all of whom are considered directors for the purposes of this
article.
All directors must be voting members of the corporation.
Each director shall serve from the time of their election until their successor
is elected and qualifies.
No director may be compensated for their service as a board member, though the
corporation may provide insurance and indemnity for board members as allowed by
law.

\subsection{Meetings}

The board of directors shall meet when necessary, provided all voting members
receive notice sent electronically at least five business days prior to the
meeting.
All voting members may attend a meeting of the board of directors.
The notice shall give the time, place, reason for calling the meeting, and the
agenda for said meeting.
Notices shall be conspicuously posted at the registered office and
electronically distributed to all members at least five business days prior to
a meeting.
Minutes shall follow the standing rules for meetings as approved at an annual
meeting.
Minutes of each board meeting shall be conspicuously posted at the registered
office and electronically distributed to members within 48 hours.
Minutes shall be considered approved when signed by all board members in
attendance.

\subsection{Elections}
\label{elections}

Each voting member present shall be given an opportunity to be a candidate for each
officer position.
If there is more than one candidate for an officer position, the candidate
which obtains the highest number votes from voting members present shall be
elected.
If there are no candidates for an officer position, the outgoing officeholder
may, if eligible, elect to serve another term or select any willing member to
serve in that position.

\subsection{Quorum}

Two thirds of the board of directors at a duly called board member meeting shall
constitute a quorum.

\subsection{Voting}

All issues, except when otherwise specified in these bylaws, shall be decided
by affirmative vote of more than one half of the directors present at a duly held
meeting.

\subsection{Resignation, Termination, and Vacancies}

Any officer or director may resign by filing a written resignation with the
Secretary or two other board members.
A Director may be removed from office only by unanimous vote of all directors
excluding the person to be removed.
Once a vote has taken place to remove a member of the board of directors no
further votes may occur to remove the director voted on until the following
annual meeting.
Vacancies on the board shall be filled at the next regular meeting using the
applicable process outlined in \ref{elections}.

Directors removed by vote of directors may qualify to run for office again
immediately after being removed from office.

\section{Committees}

\subsection{Committee formation}

The board may create committees as needed, such as fundraising, facilities,
public relations, data collection, etc.
The board chair appoints all committee chairs.

\subsection{Finance Committee}

The treasurer is the chair of the Finance Committee, which may include three
other board members.
The Finance Committee is responsible for developing and reviewing fiscal
procedures, fundraising plans, and the annual budget with Member volunteers and
other Board Members.
The board must approve the budget and all expenditures must be within budget.
Any major change in the budget must be approved by the board.
The fiscal year shall be the calendar year.
Annual reports are required to be submitted to the board showing income,
expenditures, and pending income.
The financial records of the organization are public information and shall be
made available to the membership, board members, and the public.

\subsection{Auditing Committee}

On or before September 30, the members shall nominate and approve an audit
committee consisting of three voting members who are not members of the board
of directors and have not served as a director for 180 days prior to
appointment.
The audit committee shall have full inspection rights to the affairs and
documentation of the corporation.
No audit committee shall be convened if the corporation has fewer than nine
voting members.
Otherwise, the board or voting members may not create committees or delegate
their authority.

\section{Rules and Changes to Them}
\label{rules}

\corpname{} is governed by two classes of rules: \emph{bylaws} and
\emph{policies}. You are reading the bylaws.

\subsection{Bylaws}

These bylaws may be amended only when an amendment proposal petition is signed
by more than three quarters of voting members.  Written notice of such petition
must be submitted electronically to all members.  At least 4 weeks, yet no more
than 6 months, must pass between the notification of members and the acceptance
of the bylaws change.

\subsection{Policy}

Matters deemed insufficiently solemn for placement in the bylaws will
be noted in the \emph{policy document}.  The policy document can be
amended by a simple majority of a quorum of voting members.  Written
notice of such amendment must be submitted electronically to all
members.  At least 2 weeks, yet no more than 6 months, must pass
between the notification of members and the acceptance of policy
change.


\end{document}
