\documentclass[10pt,letterpaper,titlepage]{article}
\usepackage{titletoc}

\usepackage{ifthen,varioref}
\usepackage{url}
\usepackage{titlesec}
\usepackage{fullpage}
\usepackage{hyperref}

% fix block paragraphs in toc
\usepackage{parskip}
% use block paragraphs
\setlength{\parindent}{0pt}
%\setlength{\parskip}{\baselineskip}
\setlength{\parskip}{4pt}

\newcommand\corpname{Gainesville Hackerspace, Inc.}
\newcommand\approvaldate{March 9, 2010}

\hypersetup{
    pdfauthor={Ian Taylor},
    pdftitle={\corpname{} Policies},
    pdfborder={0 0 0},
    pdfsubject={policies},
    pdfkeywords={policies, \corpname},
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue,
    bookmarks=true,
    colorlinks=false
}

\titlecontents{section}[1.5em]
    {}
    {\contentslabel{2.0em}}
    {\hspace*{-2.0em}}
    {\titlerule*[1pc]{.}\contentspage}

\renewcommand\thesection{\Roman{section}}
\renewcommand\thesubsection{\arabic{subsection}}
\titleformat{\section}{\bfseries\Large}{Article~\thesection}{0.5em}{}
\titleformat{\subsection}{\bfseries\large}{Section~\thesubsection}{0.5em}{}
\labelformat{section}{Article~#1}
\labelformat{subsection}{\protect\iscurrentsection{\thesection}Section~#1}
\newcommand\iscurrentsection[1]{%
    \ifthenelse{\equal{#1}{\thesection}}{}{Article~#1~}}

% for things like 1\st 2\nd 3\rd 4\th
\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
\renewcommand{\th}[0]{\superscript{th}}
\newcommand{\st}[0]{\superscript{st}}
\newcommand{\nd}[0]{\superscript{nd}}
\newcommand{\rd}[0]{\superscript{rd}}

\title{%
    \textsc{\LARGE \corpname \\
    \Large Policies
    }
}
\date{\today}
\author{}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{Membership}
This policy outlines the requirements of new members, and defines the method by 
which new member applications are accepted.

\subsection{Membership Requirements}

Any person meeting these requirements are eligible for membership:
\begin{itemize}
    \item 18 years or older
    \item Willing to provide documents listed in \ref{memberdocs}
    \item Payment of dues as stated in \ref{dues}
\end{itemize}

\subsection{Voting}
After an application is submitted, the Secretary shall send a notice to the 
Voting Members in a timely fashion. Voting Members shall have one (1) week from 
the date of notice to vote on the application. Votes shall be recorded by the 
Secretary, and may be submitted either in person or electronically.

For the purposes of voting on applications, quorum shall be defined as having at
least one half of the Voting Membership submitting a vote during the voting 
period.

If quorum has been met, then a simple majority of votes submitted are needed for
an application to be approved.

If quorum was not met, then the application may be resubmitted to the Voting 
Membership at the Secretary's discretion.

\subsection{Required Documents}
\label{memberdocs}

New members must provide the following before they are granted access to any 
physical locations.

\begin{itemize}
    \item Signed Liability Waiver
    \item Copy of valid proof of identity: drivers license or state/federal ID 
    card
    \item Provide current address, phone number, and emergency contact 
    information
\end{itemize}

\section{Membership Dues}
\label{dues}

New members are expected to pay first and last month's dues at joining. This
permits \corpname{} to have a little time in which to replace members.

Dues are due on or before the 15\th{} of the month.

Dues may not be waived.

\section{Meeting Schedule}

Open meetings will be held weekly, on Tuesday evening, starting at 7:00 PM.

Board meetings will be held the first Tuesday of the month, adjacent
to or during the weekly open meeting.

Membership meetings will be held the first Tuesday of the month,
adjacent to or during the weekly open meeting.

\section{Guests}
Guests are welcome on the premises so long as they are accompanied by a sponsor
member. The sponsor member is responsible for the guest while they are on
premises.

\end{document}
